### 2019-01-10 tex/manuscript.tex
added microstructure section

	\author{M. Andrew Jansen}
		\email[corresponding author, email:~]{majanse1@asu.edu}
		\affiliation{School of Life Sciences, Arizona State University, Tempe, AZ 85287, USA}
	\author{Nikhilesh Chawla}
		\affiliation{School for Engineering of Matter, Energy, and Transport, Arizona State University, Tempe, AZ 85287, USA}
	\author{Nico M. Franz}
		\affiliation{School of Life Sciences, Arizona State University, Tempe, AZ 85287, USA}

@@

@@

	Support for this hypothesis has come from three lines of evidence: 
	\begin{enumerate}
	\item Examination of the cuticle microstructure across the length of the snout has revealed consistent modification to the composite structure of the rostrum among \textit{Curculio} species.
	\item Tensile testing of the rostrum has demonstrated that the mechanical strength of the cuticle components are consistent along the length of the structure and between species.
	\item Fatigue testing has shown that a highly curved rostrum is capable of flexing hundreds of thousands of times without damage to the structure, and is apparently elastic.
	\end{enumerate}

@@

%4 sections of results ideally, nobody really uses subsections, 6 display items max.
	\section{Microstructure of the rostrum}\label{sec:microstructure} 
		Display 1: Pictures of heads, macrofiber arrangement, and exo-endo ratio at base and apex, across species.
		Explain how everything is laid out across the length of the rostrum, emphasizing that this is key to predicting and understanding the mechanical behavior of the snout during bending.
		No change in total thickness, only relative layer thickness,
		No resilin either.
		No change in total thickness, only relative layer thickness, no resilin
		outline general arrangement of normal beetle/weevil cuticle (copy/edit from previous)
		detail specifics of head capsule cuticle 
		explain modification of rostral cuticle

	\section{Tensile testing and fracture mechanics}
		The predicted behavior of the snout is borne out by the data, where UTS is strongly correlated with the cross-sectional area of the endocuticle across species.

	\section{Fatigue testing of \textit{Curculio caryae}}

%conclusion	- with intro and "results" should be no more than 3000 words
	\section{Conclusion}

@@

%50 references (as a guideline)
	\begin{thebibliography}{50}
		\section*{References}	
		\bibitem{lamport94}
			Leslie Lamport,
			\textit{\LaTeX: a document preparation system},
			Addison Wesley, Massachusetts,
			2nd edition,
			1994.

@@

%brief and 'without effusive statements'
%thank everyone who helped with data collection, especially jason (tensile testing), sridhar (if I use micro-CT scan data), dave (SEM), charlie (specimens), paige (if I use confocal data), Sal (if I use histology/staining data or confocal data, he helped with specimen clearing).
%Financial support/ funding sources/ grants.
	\begin{acknowledgements}

@@

%author contributions
%MAJ: did tensile tests, SEM, confocal (if applicable), data analysis.
%MAJ, NC: designed research, micro-CT (if applicable)
%MAJ, NMF: field collection of test specimens, procurement of specimen loans, specimen prep.
%MAJ, NC, NMF: All authors contributed to the writing, review, and revision of the manuscript.
	\section*{Author contributions}
		\begin{description}
		\item[Andrew Jansen] Conducted sectioning and staining, microscopy and imaging, tensile and fatigue testing, statistical analysis, and participated in manuscript preparation.
		\item[Nikhilesh Chawla] Facilitated microscopy, tensile and fatigue testing, and participated in manuscript preparation.
		\item[Nico Franz] Facilitated specimen acquisition and imaging, participated in manuscript preparation.
		\end{description}

>>>>

	\author{M. Andrew Jansen}
		\email[corresponding author, email:~]{majanse1@asu.edu}
		\affiliation{School of Life Sciences, Arizona State University, Tempe, AZ 85287, USA}
	\author{Jason Williams}
		\affiliation{School for Engineering of Matter, Energy, and Transport, Arizona State University, Tempe, AZ 85287, USA}
	\author{Nikhilesh Chawla}
		\affiliation{School for Engineering of Matter, Energy, and Transport, Arizona State University, Tempe, AZ 85287, USA}
	\author{Nico M. Franz}
		\affiliation{School of Life Sciences, Arizona State University, Tempe, AZ 85287, USA}

@@

%650 words here

@@

	Support for this hypothesis has come from three lines of evidence:

	\begin{enumerate}
	\item Examination of the cuticle microstructure across the length of the snout has revealed consistent modification to the composite structure of the rostrum among \textit{Curculio} species.
	\item Tensile testing of the rostrum has demonstrated that the mechanical strength of the cuticle components are consistent along the length of the structure and between species.
	\item Fatigue testing has shown that a highly curved rostrum is capable of flexing hundreds of thousands of times without damage to the structure, and is apparently elastic.
	\end{enumerate}

@@

	MIGHT BE GOOD TO SIGNPOST HERE... we discuss each of these lines of evidence in the sections below beginning with a consideration of the impact of microstructure, then we talk about mechanical testing, blah blah. Emphasize that this is key to predicting and understanding the mechanical behavior of the snout during bending.
%stick to 600 words for each results section and 500 words for conclusions
	\section{Microstructure of the rostrum}\label{sec:microstructure} %750 words here (1400 total)
		The cuticle of arthropods, including insects, is made up of chitin and numerous uncharacterized proteins, which effectively act as a matrix into which the chitin is embedded \cite{Nikolov2011,Nikolov2010,Vincent2004}.
		The cuticle is strongly influenced by its chemical properties, especially the degree of tanning and overall water content, but the arrangement of the embedded chitin fibers is primarily responsible for the its unique mechanical behavior \cite{Klocke2011,Vincent2004}.	
		Accordingly, the cuticle is often considered as a fiber-reinforced composite material; however, in beetles, the composite arrangement of the chitin fibers varies by cuticle region.

		The insect cuticle can generally be divided into three regions (Figs.~INSERT-REFS-HERE), including (1) endocuticle, which is the most compliant and innermost region; and (3) exocuticle, which is the outermost region, usually the stiffest and hardest, and coated by a waxy secretion (epicuticle) that is not of great mechanical significance in most groups.
		Between these regions lies (2) the mesocuticle, which is similar in microstructure to exocuticle, but exhibits a lesser degree of tanning (sclerotization) and usually serves as a transition zone to the endocuticle \cite{Klocke2011,Vincent1982,Vincent2004}.

		In general, these regions are confluent, and not necessarily sharply defined; for instance, the mesocuticle is not always evident, and is sometimes considered part of the exocuticle.
		In beetles, both the exocuticle and mesocuticle (when present) are laminate, and have numerous laminae of unidirectional chitin fibers, one layer thick (2-4nm each), embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other in a helicoidal arrangement, referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This microstructural arrangement allows the cuticle to exhibit transverse isotropy, or complete isotropy in some cases, despite the strong anisotropy of $\alpha$-chitin.

		Conversely, the endocuticle of Coleoptera appears to take advantage of this anisotropy to improve fracture resistance of the exoskeleton.
		Beetles in particular have a highly modified endocuticle made up of large (5-20$\mu$m OD) unidirectional bundles of chitin, called ``balken'' (German for beam, strut) or macrofibers; these macrofibers are aligned in layers, as in Figs~INSERT-FIGS-HERE \cite{Kamp2010,Kamp2015}.
		Typically, the endocuticle contains several layers of macrofibers, in which adjacent layers form pairs. 
		The layers within each pair are pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~INSERT-REFS-HERE), while the stacking angle between pairs is typically much shallower, although some other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		It is thought that this arrangement of the macrofibers contributes to the high toughness of beetle exoskeletons by inhibiting crack formation and propagation between successive layers \cite{Kamp2010,Kamp2015,Hepburn1973}.

		We have found that in \textit{Curculio}, the head capsule (as in the rest of the body) exhibits this general arrangement of the endocuticle, with an angle of approximately $30\degree$ between successive pseudo-orthogonal plies.
		Additionally, the head capsule has roughly equal thicknesses of exocuticle and endocuticle along its surface in cross section; qualitatively, manipulating this part of the head with forceps quickly reveals that this part of the head is quite rigid.

		By contrast, the region beyond the scrobe (antennal channel) is quite flexible, even in fully desiccated specimens.
		Serial thin sectioning of the snout has demonstrated that the cuticle in this region has substantially different composite properties in two key traits (see Fig~INSERT-REFS-HERE):

		\begin{enumerate}
			\item The exocuticle is reduced to a thin shell, with the endocuticle thickened to offset this reduction.
			\item The endocuticular macrofibers exhibit no rotation between successive pseudo-orthogonal plies, which are all oriented at approx. $45\degree$ to the longitudinal axis of the snout.
		\end{enumerate}

		In previous work we identified these modifications to the composite arrangement of the cuticle, but only within the species \textit{C. longinasus} Chittenden, 1927 \cite{Jansen2016, Singh2016}.
		These same modifications to the cuticle of the rostral apex have now been uncovered in a further six phylogenetically disparate species, listed below, thus indicating that this is likely a genus-wide phenomenon.

		Notably, we could find no evidence of resilin, as indicated by florescent microscopy, anywhere in the cuticle of the head (including the rostrum).
		We also observed no difference in the total thickness of the cuticle between the head capsule and rostral apex, only differences in relative layer thicknesses.
		In the next section, we demonstrate that that the endocuticle does not vary in tensile strength across the head, making it unlikely that there are significant differences in sclerotization or chitin composition within the exocuticle and endocuticle that might result in a more compliant cuticle.
		We therefor hypothesize that these differences in the microstructure of the cuticle in different regions of the head are solely responsible for the observed flexibility of the snout.

	\section{Tensile testing and fracture mechanics} %shoot for 550 words
		The predicted behavior of the snout is borne out by the data, where UTS is strongly correlated with the cross-sectional area of the endocuticle across species.

	\section{Fatigue testing of \textit{Curculio caryae}} %shot for 550 words

	\section{Conclusion} %shoot for 500 words

@@

%50 references (as a guideline, in order of appearance in text)
	\begin{thebibliography}{50}
		\section*{References}	
			\bibitem{Klocke2011}
				Klocke, D. \& Schmitz, H.
				Water as a major modulator of the mechanical properties of insect cuticle.
				\textit{Acta Biomater.}
				\textbf{7,}
				2935--2942
				(2011).

			\bibitem{Vincent1982}
				Vincent, J. F. V.
				\textit{Structural biomaterials}
				(Halsted Press,
				New York,
				1982).

			\bibitem{Vincent2004}
				Vincent, J. F. V. \& Wegst, U. G. K.
				Design and mechanical properties of insect cuticle.				
				\textit{Arthropod Struct. Dev.}
				\textbf{33:3,}
				187--199,
				(2004).

			\bibitem{Nikolov2011}
				Nikolov, S. et al.
				Robustness and optimal use of design principles of arthropod exoskeletons studied by ab initio-based multiscale simulations.
				\textit{J. Mech. Behav. Biomed. Mater.}
				\textbf{4:2,}
				129--145,
				(2011).

			\bibitem{Nikolov2010}
				Nikolov, S. et al.
				Revealing the design principles of high-performance biological composites using Ab initio and multiscale simulations: The example of lobster cuticle.
				\textit{Adv. Mater.}
				\textbf{22:4,}
				519--526,
				(2010).

			\bibitem{Blackwell1980}
				Blackwell, J. \& Weih, M.
				Structure of chitin-protein complexes: ovipositor of the ichneumon fly \textit{Megarhyssa}.
				\textit{J. Mol. Biol.}
				\textbf{137:1,}
				49--60,
				(1980).

			\bibitem{Bouligand1972}
				Bouligand, Y.
				Twisted fibrous arrangements in biological materials and cholesteric mesophases.
				\textit{Tissue Cell}
				\textbf{4:2,}
				189--217,
				(1972).

			\bibitem{Neville1976}
				Neville, A. C., Parry, D. A. \& Woodhead-Galloway, J.
				The chitin crystallite in arthropod cuticle.
				\textit{J. Cell Sci.}
				\textbf{21:1,}
				73--82,
				(1976).

			\bibitem{Cheng2009}
				Cheng, L., Wang, L., \& Karlsson, A. M.
				Mechanics-based analysis of selected features of the exoskeletal microstructure of \textit{Popillia japonica}.
				\textit{Mater. Res.}
				\textbf{24:11,}
				3253--3267,
				(2009).

			\bibitem{Hepburn1973}
				Hepburn, H. R. \& Ball, A.
				On the structure and mechanical properties of beetle shells.
				\textit{J. Mater. Sci.}
				\textbf{8:5,}
				618--623,
				(1973).

			\bibitem{Kamp2010}
				van de Kamp, T. \& Greven, H.
				On the architecture of beetle elytra.
				\textit{Entomol. Heute}
				\textbf{22,}
				191--204,
				(2010).

			\bibitem{Kamp2015}
				van de Kamp, T., Riedel, A. \& Greven, H.
				Micromorphology of the elytral cuticle of beetles, with an emphasis on weevils (Coleoptera : Curculionoidea)
				\textit{Arthropod Struct. Dev.}
				\textbf{45:1,}
				14--22,
				(2015).

@@

%brief and 'without effusive statements'
%thank everyone who helped with data collection, dave (SEM), charlie (specimens), paige (if I use confocal data), Sal (if I use histology/staining data or confocal data, he helped with specimen clearing).
%Financial support/ funding sources/ grants.
	\begin{acknowledgements}

@@

%author contributions
%MAJ: did tensile tests, SEM, confocal (if applicable), data analysis.
%MAJ, NC: designed research, micro-CT (if applicable)
%MAJ, NMF: field collection of test specimens, procurement of specimen loans, specimen prep.
%MAJ, NC, NMF: All authors contributed to the writing, review, and revision of the manuscript.
	\section*{Author contributions}
		\begin{description}
		\item[Andrew Jansen] Conducted sectioning and staining, microscopy and imaging, tensile and fatigue testing, statistical analysis, and participated in manuscript preparation.
		\item[Jason Williams] Conducted tensile and fatigue testing, participated in manuscript preparation.
		\item[Nikhilesh Chawla] Facilitated microscopy, tensile and fatigue testing, and participated in manuscript preparation.
		\item[Nico Franz] Facilitated specimen acquisition and imaging, participated in manuscript preparation.
		\end{description}
